### 2024-03-18 sections/0intro.tex

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
%
\begin{proposition*}[\ref{prop:exp_of_products_lc}]
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition*}
%
Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen-equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}). In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
\end{document}

>>>>

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \Cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
%
\begin{proposition*}[\ref{prop:exp_of_products_lc}]
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition*}
%
Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen--equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}). In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
\end{document}

### 2024-03-18 sections/1stratified.tex

\begin{example}
    The open cone $\cone(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^{k+1}_*$, which is the stratified space with stratification given by the filtration $\{0\}\subset\mathbb{R}^{k+1}$ as in \cref{ex:strat_from_filtration}.
\end{example}

@@

For topological spaces we have the concept of (\v{C}ech--Lebesgue) covering dimension $\mathsf{dim}_x (X)$ at a point $x \in X$. $C^0$ stratified spaces have an additional, related concept called depth. It plays a key role in describing these spaces.\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular. One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \cone(Z)) = \mathsf{dpt} (\cone(Z)) = \mathsf{dpt} (Z) + 1$} As the name suggests, it conveys information about how deep the stratification is. For instance, if the stratification is given by a filtration as in \Cref{ex:strat_from_CW}, then it coincides with the length of the filtration, or equivalently, with the length of the longest non-trivial chain of arrives in the stratifying poset. Similarly to $\mathsf{dim}$ it has a pointwise and a global version.

@@

Having generalized the tangent classifier to stratified manifolds we can now think about adding structure to them. The key realization is that the data which the map of spaces $B \rightarrow \mathsf{BO}(n)$ provided before was the data of a presheaf on $\mathsf{BO}(n)$, standing in as the $\infty$-category of basics with only one object $\mathbb{R}^n$. The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.

>>>>

\begin{example}
    The open cone $\cone(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^{k+1}_*$, which is the stratified space with stratification given by the filtration $\{0\}\subset\mathbb{R}^{k+1}$ as in \Cref{ex:strat_from_filtration}.
\end{example}

@@

For topological spaces we have the concept of (\v{C}ech--Lebesgue) covering dimension $\mathsf{dim}_x (X)$ at a point $x \in X$. $C^0$ stratified spaces have an additional, related concept called depth. It plays a key role in describing these spaces.\footnote{For example, we said that \Cref{thm:basics_give_basis}, as a definition, would be circular. One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \cone(Z)) = \mathsf{dpt} (\cone(Z)) = \mathsf{dpt} (Z) + 1$} As the name suggests, it conveys information about how deep the stratification is. For instance, if the stratification is given by a filtration as in \Cref{ex:strat_from_CW}, then it coincides with the length of the filtration, or equivalently, with the length of the longest non-trivial chain of arrives in the stratifying poset. Similarly to $\mathsf{dim}$ it has a pointwise and a global version.

@@

Having generalized the tangent classifier to stratified manifolds we can now think about adding structure to them. The key realization is that the data which the map of spaces $B \rightarrow \mathsf{BO}(n)$ provided before was the data of a presheaf on $\mathsf{BO}(n)$, standing in as the $\infty$-category of basics with only one object $\mathbb{R}^n$. The analogous construction in the stratified case is to provide a presheaf on $\bsc$, which by \Cref{rem:grothendieck_construction} is given by a right fibration over $\bsc$.

### 2024-03-18 sections/4gluing_alt.tex
Miniscule fix.

@@

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    A highly nontrivial check of the gluing theorem is given by the circle $S^1$. Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \mathsf{Aut} (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. This result is not generalizable to higher spheres because it uses the technology of covering spaces. \Cref{thm:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \Cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Unlike the covering space result for the circle \cite[sec.5.5]{ginot2015} which doesn't generalize to higher spheres, the gluing theorem has no such restriction. Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \Cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \mathsf{Aut} (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.

    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate triangulations of the spheres.
\end{example}

\begin{example}\label{ex:cylinder_mobius_band}
    In \Cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \Cref{prop:exp_of_products_lc} together with the results of \Cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \mathsf{Aut}_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}

>>>>

\begin{remark}
    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
\end{remark}

@@

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    A highly nontrivial check of the gluing theorem is given by the circle $S^1$. Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. This result is not generalizable to higher spheres because it uses the technology of covering spaces. \Cref{thm:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \Cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Unlike the covering space result for the circle \cite[sec.5.5]{ginot2015} which doesn't generalize to higher spheres, the gluing theorem has no such restriction. Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \Cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.

    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate traingulations of the spheres.
\end{example}

\begin{example}\label{ex:cylinder_mobius_band}
    In \Cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \Cref{prop:exp_of_products_lc} together with the results of \Cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}
